### 2023-03-03 paper/content.tex
Add changes to the complex model section of the paper

\begin{figure}[!tb]
  \centering
  \includegraphics[width=1\linewidth]{figures/simple-synthetic-data.png}
  \caption{
    Synthetic data and the various processing steps performed prior to the
    dipole moment inversion. 
    a) The synthetic noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to four dipolar sources with different
    depths and dipole moment vectors 
    (see Table~\ref{tab_synthetic_simple_results}).
    b) The upward-continued data to $z = \qty{10}{\micro\meter}$ showing
    attenuated short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all four
    sources, including the weak central source.
    e) The detected source bounding boxes (black squares) which correctly
    identify the signal of all four sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{fig_synthetic_simple_data}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=0.6\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
Comparison of true and estimated dipole magnetic moments and directions.
}
\label{fig_synthetic_simple_results}
\end{figure}

The central positions of each source obtained with ED were used as an input parameter for inverting the vertical magnetic field. The inversion produced a least squares approximation solution for the vector of Cartesian
magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions (D and I) and intensity of magnetic moment $m$ (Fig.~\ref{fig_synthetic_simple_results}). We also obtained the uncertainty propagation of this inversion, using equations~\ref{chi_square}-\ref{uncertanties}, as shown in the Table~\ref{tab_synthetic_simple_results}.

@@

This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of 2000 x 2000 $\mu
m$. The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$ spacing and 5 $\mu m$ sample-sensor distance. For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensity. The depths vary between 1 and 20 $\mu m$, while the
magnetic moment intensity range from $10^{-13}$ to $10^{-15}$ $A/m^2$.

To add more complexity, we simulate two stable magnetization  directions, both sampled from a pseudo-random Gaussian distribution, this randomness simulates the NRM found in real ferromagnetic particles that
vary individually but average out to the inducing field direction. The first group of sources ($n = 70$) has a magnetization mean direction of D = 0°, I = 0°, and a standard deviation of 5°. While the second one ($n = 30$) has a magnetization mean direction of D = 180°, I = 0°, and a standard deviation of 5°. Finally, we contaminated the data with high-frequency normally-distributed pseudo-random
noise with zero means and 20 nT standard deviations, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain. The noise-corrupted synthetic $b_z$ image is shown in
Figure~\ref{complex-synthetic-data}a.

\begin{figure}[t]
  \centering
  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
  \caption{
    a) Complex synthetic data contaminated with  both high and low frequencies noise. b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.
  }
  \label{complex-synthetic-data}
\end{figure}

Since now the data have both high and low-frequency noise, we performed a $3^{rd}$ degree polynomial fitting to remove the low-frequency wavelength from the signal. Subsequently, we applied an upward continuation to get rid of the high-frequency ones (Fig.~\ref{complex-synthetic-data}b). Followed by the TGA map calcultaion (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e). The result of the source's window detection method is shown in Figure~\ref{complex-synthetic-data}e,
where 97 particles out of the original 100 were detected.

@@

\textbf{FROM HERE!}

Figure~\ref{P8gMJ9mWpS} shows the difference between the estimated dipole
moments and the true values for each of the 84 particles that were identified.
Figure~\ref{P8gMJ9mWpS}c shows the R² coefficient of determination representing
how well the dipolar model is able to fit the observed data in the given
window. The depth and radius of each particle are represented by horizontal and
vertical cross bars, respectively. The depth and radius are useful proxies for
the width and amplitude of the magnetic signal of each particle, which is
crucial to know when evaluating the inversion results.

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\linewidth]{figures/complex-synthetic-comparison.png}
\caption{
The validation of the result obtained with the inversion was calculated for
each individual particle based on the error between the real parameters modeled
and their respective recovered values, being (a) the direction and (b)
intensity of the magnetic moment, in addition to the R$^2$ score (c) obtained
by comparing the forward model and the actual data. The depth and radius of the
magnetic sources are also important factors that influence the final result,
therefore, these data are given in the form of cross plots, with the vertical
bar represented by the depth (1 - 19 $\\mu m$) and the horizontal bar by the
radius (0.01 - 0.95 $\\mu m$).
}
\label{complex-synthetic-comparison}
\end{figure}

The application in complex synthetic data allows observing the strengths and
limitations of the proposed methodology. Some of the strengths that can be
mentioned are: (i) the applied technique not only detects most of the modeled
sources but also (ii) most of the recovered magnetic parameters have
considerably low errors, especially in the directions, usually less than 5°
(Figure~\ref{complex-synthetic-comparison}a). (iii) The magnetic moments obtained also tend to
not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when
R\textsuperscript{2} scores are high (\textgreater 0.95)
(Figure~\ref{complex-synthetic-comparison}c). (iv) Shallow particles grouped in clusters are
usually well individualized during window selection, as well as (v) some
particles that produce a weak magnetic signal but isolated particles.

The main limitations observed are: (i) the blob detection fails when there are
sources too close, grouping them into the same window, thus causing an
erroneous result both for Euler deconvolution and for the magnetic parameters.
(ii) The very same occurs when there is a source under another, in this case,
the magnetic signal is the sum of both. (iii) In clusters of larger and/or
deeper particles, although the method individualizes them well, the magnetic
signal of the neighboring particles can considerably influence the result of
the inversion. Apparently, there is a direct relationship between the size and depth with the observed errors. It is clear from the cross bars in
Figure~\ref{P8gMJ9mWpS} that deep particles and/or particles with small radii
generate worse results essentially because they will produce smaller anomalous
fields in the magnetic maps. Note nonetheless that even small particles when
close to the surface are adequately modeled by our method.

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\linewidth]{figures/complex-synthetic-fitting-test.png}
\caption{
a)
}
\label{complex-synthetic-fitting-test}
\end{figure}

Figure~\ref{RDs2vUEqCI} shows stereoplots with the directions generated by the
model and the recovered data. The mean directions modeled are coincident with
the model and the distribution is coincident within the 95\% confidence cone.
When filtered to include only data with R\textsuperscript{2} \textgreater 0.95
the obtained directions are closer to the model average and less sparse.

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\linewidth]{figures/complex-synthetic-stereograms.png}
\caption{
a) Simulation of a thin section of rock with particles uniformly magnetized in
the average direction of the induced field
45{\textbackslash}textdegree/45{\textbackslash}textdegree. b) The recovered
data, without any type of filtering, are sparse, but statistically generate the
same average direction. c) It is still possible to filter only the directions
of the magnetic sources with the best fitting determined by the coefficient of
determination ($R^ 2 \\geq 0.95$) to ensure better grouping of the directions
around the mean value.
}
\label{complex-synthetic-stereograms}
\end{figure}

@@

In order to provide two distinct directions associated with the different
magnetic mineral types in this sample, we applied two IRM pulse fields of 2.7 T
and 0.3 T, respectively toward the +X and -X directions. In this way, the high
coercivity grains (hematite) would point towards +X and the low coercivity ones
(magnetite) would align in the -X direction.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{figures/RealDataStereo.png}
\caption{
a) The recovered data, without any type of filtering. b) Recovered data
filtered by the coefficient of determination ($R^ 2 \\geq 0.7$), which shows
two clusters of direction located on each pole of the stereogram.
}
\label{nkoamthawa}
\end{figure}

@@

the same authors showed that particles in the single vortex PSD state present
more accurate inversion results when considering the non-dipole components for
small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor
distances the dipole as approximations are remarkably accurate, as the
higher-order moments decay rapidly with distance and therefore have less
influence on the particle's magnetic signal. Thus, our approach can be
considered reasonable for working with particle signals in SD (already a
dipole) and PSD states. The latter happens due to the QDM sensor height being
usually greater than 5 $\\mu m$, considering a particle on the immediate
surface of the sample the higher-order moments are already quite attenuated.\}

>>>>

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/simple-synthetic-data.png}
  \caption{
    Synthetic data and the various processing steps performed prior to the
    dipole moment inversion. 
    a) The synthetic noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to four dipolar sources with different
    depths and dipole moment vectors 
    (see Table~\ref{tab_synthetic_simple_results}).
    b) The upward-continued data to $z = \qty{10}{\micro\meter}$ showing
    attenuated short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all four
    sources, including the weak central source.
    e) The detected source bounding boxes (black squares) which correctly
    identify the signal of all four sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{fig_synthetic_simple_data}
\end{figure}

@@

\begin{figure}[tb!]
\centering
\includegraphics[width=0.5\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
Comparison of true and estimated dipole magnetic moments and directions.
}
\label{fig_synthetic_simple_results}
\end{figure}

The central positions of each source obtained with ED were used as an input parameter for inverting the vertical magnetic field. The inversion produced a least squares approximation solution for the vector of Cartesian magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions (D and I) and intensity of magnetic moment $m$ (Fig.~\ref{fig_synthetic_simple_results}). We also obtained the uncertainty propagation of this inversion, using equations~\ref{chi_square}-\ref{uncertanties}, as shown in Table~\ref{tab_synthetic_simple_results}.

@@

This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of 2000 x 2000 $\mu m$. The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$ spacing and 5 $\mu m$ sample-sensor distance. For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensity. The depths vary between 1 and 20 $\mu m$, while the magnetic moment intensity range from $10^{-12}$ to $10^{-14}$ $Am^2$.

To add more complexity, we simulate two stable magnetization  directions, both sampled from a pseudo-random Gaussian distribution, this randomness simulates the NRM found in real ferromagnetic particles that vary individually but average out to the inducing field direction. The first group of sources ($n = 70$) has a magnetization mean direction of D = 0°, I = 0°, and a standard deviation of 10°. While the second one ($n = 30$) has a magnetization mean direction of D = 180°, I = 0°, also with standard deviation of 10°. Finally, we contaminated the data with high-frequency normally-distributed pseudo-random noise with zero means and 50 nT standard deviations, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain. The noise-corrupted synthetic $b_z$ image is shown in Figure~\ref{complex-synthetic-data}a.

\begin{figure}[t]
  \centering
  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
  \caption{
    a) The synthetic high and low-frequency noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated. 
    b) Residual anomaly map after the $5^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all sources, especially the weaker ones.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the signal of the sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{complex-synthetic-data}
\end{figure}

Since now the data have both high and low-frequency noise, we performed a $5^{th}$ degree polynomial fitting to remove the low-frequency wavelength from the signal. Subsequently, we applied an upward continuation to get rid of the high-frequency ones (Fig.~\ref{complex-synthetic-data}b). Followed by the TGA map calculation (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e). The positioning result of each source by window detection method is shown in Figure~\ref{complex-synthetic-data}e, where 98 particles out of the original 100 were detected.

@@

Figure~\ref{complex-synthetic-comparison} shows the difference between the estimated dipole moments and the true values for each of the 97 particles that were identified and the model fitting tests. Firstly, we evaluate the magnetic direction misfits by calculating the module of the angular difference between the true and the estimated magnetization vectors (Fig.~\ref{complex-synthetic-comparison}a). Afterward, we calculate the dipole moment misfits in percentage (~$|~100 \left( m_{true} - m_{estimate}\right)~/~\left(m_{true}\right)~|$~), as shown in Figure~\ref{complex-synthetic-comparison}b). Then, the fitting tests were performed using the equations~\ref{R2}-~\ref{SNR} in an attempt to select which criterion best separates data with good fitting and low errors of direction and dipole moment. Figure~\ref{complex-synthetic-comparison}c shows the R² coefficient, or the \emph{D} parameter of the non-dipolarity test \citep{Fu2020}, representing how well the dipolar model is able to explain the observed data in the given window. On the other hand, the SNR is capable to express the power of the predicted model over its residual, therefore can select which sources are more "visible" by the sensor (Fig.~\ref{complex-synthetic-comparison}d). Consequently yielding results directly proportional to the R² coefficient.

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.75\linewidth]{figures/complex-synthetic-comparison.png}
\caption{
The validation of the result obtained with the inversion was calculated for each individual particle based on the error between the real parameters modeled and their respective recovered values, being (a) the direction and (b) intensity of the magnetic moment, in addition to the $R^2$ score (c) obtained by comparing the forward model and the actual data. The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 20 $\mu m$) and the horizontal bar by the dipole moment amplitude ($10^{-12}$ to $10^{-14}$ $Am^2$).
}
\label{complex-synthetic-comparison}
\end{figure}

The depth and dipolar moment of each particle are represented by horizontal and vertical error bars (Fig.~\ref{complex-synthetic-comparison}), respectively. These two variables are useful proxies for reliably determining the range for the width and amplitude range of the vertical component magnetic signal the technique is able to identify, which is crucial to know when evaluating these types of inversion results.
The application in complex synthetic data allows observing the strengths and limitations of the proposed methodology. Some of the strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a). (iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Fig.~\ref{complex-synthetic-comparison}b) when R\textsuperscript{2} and SNR scores are high (e.g., $\geq 0.95$ and $\geq 10$, respectively) (Fig.~\ref{complex-synthetic-comparison}c-d). (iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some particles that produce a weak magnetic signal but isolated particles.

The main limitations observed are: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters. (ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both. (iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion. Apparently, there is a direct relationship between the dipole intensity and depth with the observed errors. It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep particles and/or particles with small magnetic intensity generate worse results essentially because they will produce smaller anomalous fields in the magnetic maps. Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise.

%\begin{figure}[!htbp]
%\centering
%\includegraphics[width=1\linewidth]{figures/complex-synthetic-fitting-test.png}
%\caption{
%a)
%}
%\label{complex-synthetic-fitting-test}
%\end{figure}

Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each sources. The distribution of the estimated directions are coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window. When filtered to include only data with R\textsuperscript{2} \textgreater 0.95 and SNR \textgreater 10 the obtained direction distribution closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).

\begin{figure}[htbp!]
\centering
\includegraphics[width=1\linewidth]{figures/complex-synthetic-stereograms.png}
\caption{
a) Simulation of a thin section of rock with two sets of stable particles uniformly magnetized in the average direction of the induced field (0{\textbackslash}textdegree/0{\textbackslash}textdegree and 180{\textbackslash}textdegree/0{\textbackslash}textdegree. b) The estimated vector directions without any type of filtering. c) Filtering criteria to select the sources' magnetic directions with the best fitting determined by the coefficient of determination ($R^ 2 \geq 0.95$) and signal-to-noise ratio (SNR $ \geq 10$).
}
\label{complex-synthetic-stereograms}
\end{figure}

@@

In order to provide two distinct directions associated with the different
magnetic mineral types in this sample, we applied two IRM pulse fields of 2.7 T
and 0.3 T, respectively toward the +Y and -Y directions. In this way, the high
coercivity grains (hematite) would point towards +Y and the low coercivity ones
(magnetite) would align in the -Y direction.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{figures/RealDataStereo.png}
\caption{
a) The recovered data, without any type of filtering. b) Recovered data
filtered by the coefficient of determination ($R^ 2 \geq 0.7$), which shows
two clusters of direction located on each pole of the stereogram.
}
\label{nkoamthawa}
\end{figure}

@@

the same authors showed that particles in the single vortex PSD state present
more accurate inversion results when considering the non-dipole components for
small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor
distances the dipole as approximations are remarkably accurate, as the
higher-order moments decay rapidly with distance and therefore have less
influence on the particle's magnetic signal. Thus, our approach can be
considered reasonable for working with particle signals in SD (already a
dipole) and PSD states. The latter happens due to the QDM sensor height being
usually greater than 5 $\mu m$, considering a particle on the immediate
surface of the sample the higher-order moments are already quite attenuated.
